### 2019-04-22 Manuscript/Manuscript.tex

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{Manuscript/Figures/LIP_Areas.pdf}
	\caption{\textbf{A)} LIPs included in this analysis. The size of each circle reflects the initial area estimate of each LIP. The + indicates the timing and absolute paleolatitude of the centroid of each LIP at the time of emplacement. Car.-Col. = Caribbean-Colombian. \textbf{B)} Total LIP area through time for the different post-emplacent scenarios. Only the `no decay' scenario excludes pre-Phanerozoic LIPs. \textbf{C)} Tropical LIP area through time for the different post-emplacement scenarios. The arrows to the right indicate reconstructed tropical LIP area at the time of emplacement for the ca. 720 and 1109~Ma Franklin and Umkondo LIPs. The triangles show the paleogeographic reconstruction times in Fig. \ref{fig:Reconstruction_Snapshots}. \textbf{D)} Contour plot showing the latitudinal distribution of LIP area for the preferred post-emplacement model. \textbf{E)} Latitudinal extent of land ice away from the poles \citep{Macdonald2019a} and compilation of \textit{p}CO$_{2}$ proxies \citep{Foster2017a} (\textit{p}CO$_{2}$ y-axis reversed, and in log-scale). Error bars indicate standardized uncertainties, and grey bands indicate 68 and 95\% confidence intervals for Monte Carlo resampled LOESS fits through the \textit{p}CO$_{2}$ proxy data \citep{Foster2017a}.}
	\label{fig:LIP_Areas}
\end{center}
\end{figure}

>>>>

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off,font=small]{caption}

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{Manuscript/Figures/LIP_Areas.pdf}
	\caption{\textbf{A)} LIPs included in this analysis. The size of each circle reflects the initial area estimate of each LIP. The + indicates the timing and absolute paleolatitude of the centroid of each LIP at the time of emplacement. Car.-Col. = Caribbean-Colombian. \textbf{B)} Total LIP area through time for the different post-emplacent scenarios. Only the `no decay' scenario excludes pre-Phanerozoic LIPs. \textbf{C)} Tropical LIP area through time for the different post-emplacement scenarios. The arrows to the right indicate reconstructed tropical LIP area at the time of emplacement for the ca. 720 and 1109~Ma Franklin and Umkondo LIPs. The triangles show the paleogeographic reconstruction times in Fig. \ref{fig:Reconstruction_Snapshots}. \textbf{D)} Contour plot showing the latitudinal distribution of LIP area for the preferred post-emplacement model. \textbf{E)} Latitudinal extent of land ice away from the poles \citep{Macdonald2019a} and compilation of \textit{p}CO$_{2}$ proxies \citep{Foster2017a} (\textit{p}CO$_{2}$ y-axis reversed, and in log-scale). Error bars indicate standardized uncertainties, and grey bands indicate 68 and 95\% confidence intervals for Monte Carlo resampled LOESS fits to the \textit{p}CO$_{2}$ proxy data \citep{Foster2017a}. Note that there are \textit{p}CO$_{2}$ estimates \textless100~ppm that are cut off in this plot.}
	\label{fig:LIP_Areas}
\end{center}
\end{figure}
